\section{Instrument Data Description}
\label{DATA}

\pipename,, data can be separated into {\it raw} frames and {\it product} frames.
Raw frames are the unprocessed output of the \pipename,, instrument observations,
while product frames are either the result of the \pipename,, pipeline processing 
(as reduced frames, master calibration frames, etc.), or are outsourced (as 
standard stars catalogs, lists of grism characteristics, etc.).

Any raw or product frame can be classified on the basis of a set of keywords 
read from its header. Data classification is typically carried out by the 
DO or by \ {\it Gasgano} [7], that apply the same set of classification
rules. The 
association of a raw frame with calibration data ($e.g.$, of a science 
frame with a master bias frame) can be obtained by matching the values 
of a different set of header keywords.

Each kind of \ raw \ frame is typically associated to a single \pipename,,
pipeline recipe, {\it i.e.}, the recipe assigned to the reduction of that
specific frame type. In the pipeline environment this recipe would 
be launched automatically. In some cases two recipes are assigned,
one meant for the reduction of a single frame of that type, and the
other for the reduction of a \ {\it stack} \ of frames of the same 
type, as happens in the case of nodding science observations. 

A \ product \ frame may be input to more than one \pipename,, pipeline recipe, 
but it may be created by just one pipeline recipe (with the same
exceptions mentioned above). In the automatic pipeline environment a 
product data frame alone wouldn't trigger the launch of any recipe.

In the following all raw and product \pipename,, data frames are listed,
together with the keywords used for their classification and 
correct association. The indicated {\it DO category} is a 
label assigned to any data type after it has been classified,
which is then used to identify
the frames listed in the {\it Set of Frames} (see Section
\ref{SOF}, page \pageref{SOF}).

\label{DATA:RAW}

Raw frames can be distinguished in {\it general} frames, {\it direct imaging}
frames, {\it MOS} frames and {\it IFU} frames. Their intended use is
implicitly defined by the assigned recipe.




