\documentclass[pdftex,a4paper,twoside,11pt]{article}
\NeedsTeXFormat{LaTeX2e}
% check whether we are running pdflatex
\usepackage[dvips]{graphicx}
\usepackage{picinpar}
\usepackage{float}
\usepackage{graphics}
\usepackage{varioref}
\usepackage{natbib}
\usepackage{afterpage}
\usepackage[usenames,dvipsnames]{color}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{red}{rgb}{1,0,0}
\definecolor{green}{rgb}{0,1,0}
\definecolor{orange}{rgb}{1,0.5,0}

\newcommand{\black}[1]{\color{black}{#1}\color{black}\ }
\newcommand{\yellow}[1]{\color{yellow}{#1}\color{black}\ }
\newcommand{\red}[1]{\color{red}{#1}\color{black}\ }
%\newcommand{\green}[1]{\color{green}{#1}\color{black}\ }

\newif\ifpdf
  \ifx\pdfoutput\undefined
    \pdffalse            % we are not running pdflatex
  \else
    \pdfoutput=1         % we are running pdflatex
    \pdfcompresslevel=9  % compression level for text and image;
    \pdftrue
\fi

\ifpdf  % stuff to do only if we are running pdflatex
  %include hyperref for pdf
  \usepackage[pdftex,colorlinks=true,
                     pdfstartview=FitV,
                     linkcolor=darkblue,
                     citecolor=darkblue,
                     urlcolor=darkblue,
                     plainpages=false,
                     pdfpagelabels,
                     linktocpage,
                     backref,pagebackref]{hyperref}
%  \usepackage{thumbpdf}
%  \pdfinfo{%
%     /Title      (Reflex XShooter Tutorial)
%     /Author     (Daniel Bramich, Sabine Moehler)
%     /Keywords   (ESO Manual)
%  }
\fi

\hypersetup{
pdfpagemode = {None}, % Verhindert die automatische Anzeige der Lesezeichen
pdftitle = {Reflex IIINSTRUMENT Tutorial},
pdfauthor = {Name Surname},
pdfsubject= {Reflex IIINSTRUMENT Tutorial}
}

%% Include layout, additional commands and abbreviations
\graphicspath{{../figures/}{../pipedoc_common/figures/}}
\input{layout}
\input{shortcut}

%% Remember to update shortcut.tex
\def\reldate{\releasedate}
\def\pipeno{\pipelinevers}
\def\kitno{\pipeno}
\def\docno{\pipelinemanualvers}
\def\qfitsno{\qfitsvers}
\def\cplno{\cplvers}
\def\esorexno{\esorexvers}
\def\reflexno{\reflexvers}
\def\gasganono{\gasganovers}
\def\jdkno{\jdkvers}
\def\dmdissue{\docno}

\dmdTitle{Reflex IIINSTRUMENT Tutorial}
\dmdDocId{VLT-MAN-ESO-19500-....}
\dmdIssue{0.1}
\dmdDate{\releaseday}

\dmdPreparedBy{N. Surname}
\dmdPreparedOn{\releaseday}
\dmdApprovedBy{N. Surname}
\dmdApprovedOn{}
\dmdReleasedBy{N. Surname}
\dmdReleasedOn{}

\setlongtables
\makeindex
\bibliographystyle{plain} 

\begin{document}
\pagenumbering{arabic}
\dmdmaketitle
\emptypage{This page was intentionally left blank}

\begin{center}
  \textbf{Change record}

  \tablehead{\hline
    \multicolumn{1}{|c|}{Issue/Rev.}\tbspa &
    \multicolumn{1}{|c|}{Date} &
    \multicolumn{1}{|c|}{Section/Parag.\ affected} &
    \multicolumn{1}{|c|}{Reason/Initiation/Documents/Remarks}\tbspb \\
    \hline}
  \tabletail{\hline}

  \begin{supertabular}{|l|l|l|l|}
    1.0\tbspa    & 25/09/2012 & All & Beta release   \\
%    1.1\tbspa    & 20/03/2012 & All & Comments from Beta release   \\
%    2.0\tbspa & \releasetime & Updated details & Update\\
  \end{supertabular}
\end{center}
\emptypage{This page was intentionally left blank}

\tableofcontents
\cleardoublepage

\input{reflex_intro_scope.tex} %This file is in the pipedoc_common directory

Add here some explanation about this specific workflow. Instrument modes supported, etc...

\input{reflex_wkf_installation} %This file is in the pipedoc_common directory

\section{Demo Data}
Add some explanation about the demo data used.

\section{Quick Start: Reducing The Demo Data \label{sec:quick_start}}

Add here a two pages maximum explanation on how to quickly reduce the demo data set.

\input{reflex_about_canvas} %This file is in the pipedoc_common directory
\input{reflex_wkf_general_desc} %This file is in the pipedoc_common directory
\subsection{Workflow Actors}
\input{reflex_simple_actors} %This file is in the pipedoc_common directory

Add here a description of this workflow specific actors 
(probably including some composite actors).

\input{reflex_lazy_mode} %This file is in the pipedoc_common directory

Add here a description of the workflow steps like Data organisation,
routing, creation of calibration files and science reduction.

Add here a description on how to optimise the results of the workflow.

\input{reflex_faq.tex}

Add here a section on troubleshooting problems.

\bibliography{iiinstrumentpdoc}
\end{document}
