\section{Installation}
\label{sec:installation}

% \red{\textit{Installation instructions for the different package types offered
%                 by ESO and build instructions for experienced users. This part will be
%                 filled by ESO to a large extent.}}

\subsection{System Requirements}
\label{sec:platforms}

\subsection{Installation}
\label{sec:install-howto}

For Fedora, CentOS, Scientific Linux users within ESO, you can use the RPM
installation.
For that, you need to refer to the RPM installation instructions:
{\it http://eso.org/sci/software/pipelines/installation/rpm.html}

The CR2RES pipeline is not public yet, therfore you will need to setup the
repositories to a different place:
USE 'devel' instead of 'stable' !

For example:

sudo dnf config-manager
--add-repo=ftp://ftp.eso.org/pub/dfs/pipelines/repositories/stable/fedora/esore
po.repo

needs to be replaced by:

sudo dnf config-manager
--add-repo=ftp://ftp.eso.org/pub/dfs/pipelines/repositories/devel/fedora/esorep
o.repo

For any other system, or if you are outside ESO, you will need to download the
installation script, and run it on your computer:

\begin{itemize}
        \item Create an new directory and change to it
        \item Download {\it http://eso.org/sci/software/pipelines/install\_pipelinekit}
              and change its permission to execute ({\it chmod u+x install\_pipelinekit})
        \item Download the CR2RES package from

                      {\it
                              ftp://ftp.eso.org/pub/dfs/pipelines/kit\_devel/cr2re-kit-0.5.0-2\_svn232540\_he
                              ad.tar.gz}
        \item Execute {\it ./install\_pipelinekit
              cr2re-kit-0.5.0-2\_svn232540\_head.tar.gz}

              The execution scipt will ask you where to install the package. I recommend to
              have a local installation in order to easily update at a later stage.

              Questions asked by the installation script:
              \begin{itemize}

                      \item Where should I install the software packages ?

                            Use a new directory (e.g. /home/user/cr2res\_install)

                      \item Where should I install the pipeline calibration files ?

                            Use a subdirectory (e.g. /home/user/cr2res\_install/cdb)

                      \item Configuration
              \end{itemize}

        \item Configuration

              \begin{itemize}
                      \item esorex is installed here : /home/user/cr2res\_install/bin/esorex
                            Make sure it is in your path.

                      \item The CR2RES recipes are installed under :
                            /home/user/cr2res\_install/lib/esopipes-plugins/cr2re-0.5.0
                            esorex needs to be configured to know where th CRI2RES recipes are
                            installed. This is done through the recipe-dir parameter.
                            Please update :

                            esorex.caller.recipe-dir=/home/user/cr2res\_install/lib/esopipes-plugins/cr2re-
                            0.5.0
                            in the esorex configuration file (usually \$HOME/.esorex/esorex.rc)

                      \item If you do not have any esorex configuration file, you can run
                            esorex --create-config
                            to create a default one.

                      \item You know you are all set when running
                                    {\it esorex --recipes}
                            gives you the list of installed recipes.

              \end{itemize}
\end{itemize}

If you want to install a new version, simply remove the directory
/home/user/cr2res\_install and start again.

\subsection{Building the CR2RES Pipeline}
\label{sec:compile-howto}

\subsubsection{Build Requirements}
\label{sec:compile-requirements}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: